### 2021-04-13 02_abstract/abstract.tex
Updated lines of code change in ESMValTool

To overcome these issues of single-process-oriented emergent constraints, an
alternative approach based on \acfAbstract{ML} is introduced. Since this new
technique relies on a large number of data points to train the \acs{ML}
algorithm, the scalar climate sensitivity expressed as \acs{ECS} or \acs{TCR}
is not an appropriate target variable. Therefore, \acfAbstract{GPP} as a
process that contributes to climate sensitivity is studied as an alternative.
\acs{GPP} is the largest flux of the terrestrial carbon uptake and slows down
global warming by removing \acs{CO2} from the atmosphere. In this analysis, an
existing emergent constraint on \acs{CO2} fertilization is combined with an
\acs{ML} approach to constrain the spatial variations of multi-model \acs{GPP}
projections. In the first step of the two-step approach, observed changes in
the \acs{CO2} seasonal cycle at \acl{KUM} are used to constrain the global mean
\acs{GPP} at the end of the \nth{21} century (\range{2091}{2100}) in \acl{RCP}
8.5 simulations with \acsp{ESM} participating in \acs{CMIP}5 to
$\pmrangeunit{171}{12}{\GtCyr{}}$, compared to the unconstrained model range
$\rangeunit{156}{247}{\GtCyr{}}$. In a second step, an \acs{ML} model is used
to constrain gridded future absolute \acs{GPP} and gridded fractional \acs{GPP}
change in two independent approaches. For this, observational data is fed into
the \acs{ML} algorithm that has been trained on \acs{CMIP}5 data to learn
relationships between present-day physically relevant diagnostics and the
target variable. In a leave-one-model-out \acl{CV} approach, the \acs{ML} model
shows superior performance to the \acs{CMIP}5 \acs{MMM}. The new approach
predicts a higher \acs{GPP} increase in high latitudes and a lower \acs{GPP}
increase in regions closer to the equator.

>>>>

To overcome these issues of single-process-oriented emergent constraints, an
alternative approach based on \acfAbstract{ML} is introduced. Since this new
technique relies on a large number of data points to train the \acs{ML}
algorithm, the scalar climate sensitivity expressed as \acs{ECS} or \acs{TCR}
is not an appropriate target variable. Therefore, \acfAbstract{GPP} as a
process that contributes to climate sensitivity is studied as an alternative.
\acs{GPP} is the largest flux of the terrestrial carbon uptake and slows down
global warming by removing \acs{CO2} from the atmosphere. In this analysis, an
existing emergent constraint on \acs{CO2} fertilization is combined with an
\acs{ML} approach to constrain the spatial variations of multi-model \acs{GPP}
projections. In the first step of the two-step approach, observed changes in
the \acs{CO2} seasonal cycle at \acl{KUM} are used to constrain the global mean
\acs{GPP} at the end of the \nth{21} century (\range{2091}{2100}) in
\acfAbstract{RCP} 8.5 simulations with \acsp{ESM} participating in \acs{CMIP}5
to $\pmrangeunit{171}{12}{\GtCyr{}}$, compared to the unconstrained model range
of $\rangeunit{156}{247}{\GtCyr{}}$. In a second step, an \acs{ML} model is
used to constrain gridded future absolute \acs{GPP} and gridded fractional
\acs{GPP} change in two independent approaches. For this, observational data is
fed into the \acs{ML} algorithm that has been trained on \acs{CMIP}5 data to
learn relationships between present-day physically relevant diagnostics and the
target variable. In a leave-one-model-out \acl{CV} approach, the \acs{ML} model
shows superior performance to the \acs{CMIP}5 \acs{MMM}. The new approach
predicts a higher \acs{GPP} increase in high latitudes and a lower \acs{GPP}
increase in regions closer to the equator.

### 2021-04-13 ch03_esmvaltool/esmvaltool.tex
Updated lines of code change in ESMValTool

As of \TheMonth{}, 40408 lines of code have been added and 21050 lines of code
have been removed from the GitHub repository of \ac{ESMValCore} by the author
of this thesis. Apart from general improvements of the code base, these changes
and additions mainly include new preprocessor functions that can be applied to
the input data and derivation scripts for new non-\ac{CMOR} variables.
\Cref{tab:03:changes_to_esmvalcore} shows a summary of these main
contributions, which are partly published in the scientific documentation of
\ac{ESMValCore} \autocite{Righi2020}.

@@

In addition to the analyses presented in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs,ch:06:paper_gpp}, several
more recipes and \acs{CMOR}ization scripts for observational data have been
added to the main \ac{ESMValTool} repository on GitHub. A summary of these is
given in \cref{tab:03:changes_to_esmvaltool}. Moreover, multiple minor changes
and additions have been implemented to improve the code base and/or to fix
bugs. In total, the author of this study has added 88668 lines of code and
removed 47816 lines of code from the \ac{ESMValTool} repository (as of
\TheMonth{}). Parts of these implementations are already published in the
scientific documentation of the \ac{ESMValTool}, which covers large-scale
diagnostics \autocite{Eyring2020}, diagnostics for emergent constraints and
future projections \autocite{Lauer2020}, and diagnostics for extreme events and
regional evaluation \autocite{Weigel2020}.

>>>>

As of \TheMonth{}, 41780 lines of code have been added and 21713 lines of code
have been removed from the GitHub repository of \ac{ESMValCore} by the author
of this thesis. Apart from general improvements of the code base, these changes
and additions mainly include new preprocessor functions that can be applied to
the input data and derivation scripts for new non-\ac{CMOR} variables.
\Cref{tab:03:changes_to_esmvalcore} shows a summary of these main
contributions, which are partly published in the scientific documentation of
\ac{ESMValCore} \autocite{Righi2020}.

@@

In addition to the analyses presented in
\cref{ch:04:papers_ecs_tcr_assessment,ch:05:paper_ecs,ch:06:paper_gpp}, several
more recipes and \acs{CMOR}ization scripts for observational data have been
added to the main \ac{ESMValTool} repository on GitHub. A summary of these is
given in \cref{tab:03:changes_to_esmvaltool}. Moreover, multiple minor changes
and additions have been implemented to improve the code base and/or to fix
bugs. In total, the author of this study has added 98662 lines of code and
removed 49823 lines of code from the \ac{ESMValTool} repository (as of
\TheMonth{}). Parts of these implementations are already published in the
scientific documentation of the \ac{ESMValTool}, which covers large-scale
diagnostics \autocite{Eyring2020}, diagnostics for emergent constraints and
future projections \autocite{Lauer2020}, and diagnostics for extreme events and
regional evaluation \autocite{Weigel2020}.

### 2021-04-13 end_acknowledgments/acknowledgments.tex
Updated lines of code change in ESMValTool

First of all, I would like to express my sincere gratitude to my supervisor and
primary examiner, \Prof{} \Dr{} Veronika Eyring. Without her continuous support
and advice, patience, motivation, and expertise, this \PhD{} project would not
have been possible. I further thank her for providing me the opportunity to
visit many international conferences, which allowed me to meet amazing people
and collaborate with colleagues from all over the world.

I am grateful to my second examiner, \Prof{} \Dr{} Pierre Gentine, for his
great advice and comments on my work.

My sincere thanks go to all my co-authors of my first-author studies, namely
\Prof{} \Dr{} Gustau Camps-Valls, \Prof{} \Dr{} Veronika Eyring, \Prof{} \Dr{}
Pierre Friedlingstein, \Prof{} \Dr{} Pierre Gentine, \Dr{} Axel Lauer, \Prof{}
\Dr{} Markus Reichstein, and \Prof{} \Dr{} Steven Sherwood, for their advice,
feedback, and collaboration.

I would like to thank \Prof{} \Dr{} Gustau Camps-Valls and his Image and Signal
Processing (ISP) group for hosting me during my research stay at the University
of Valencia. I really enjoyed the time in Valencia, where I had the opportunity
to meet great people and expand my knowledge about \acl{ML}.

Many thanks to \Dr{} Axel Lauer for being an amazing second author and for the
endless patience he showed whenever I had questions for him. I am also very
grateful to \Dr{} Birgit Hassler for her advice in all circumstances and for
providing the urgently-needed chocolate and cookies during long hours in the
office. A warm thank you to all my colleagues at DLR-EVA and IUP for their
professional advice, helpful discussions, and the great time we spent together
inside and outside of the office.

A special thank you to the \ac{ESMValTool} core development team for providing
me useful insights into modern software development and for the great workshops
and beers we shared together.

@@

A very special thanks to the (extended) Langer family for their advice and
support in all situations of life.

>>>>

First of all, I would like to express my sincere gratitude to my supervisor and
primary examiner, \Prof{} \Dr{} Veronika Eyring. Without her continuous
support, advice, enthusiasm, expertise, and patience, this \PhD{} project would
not have been possible. I further thank her for providing me the opportunity to
visit many international conferences, which allowed me to meet amazing people
and collaborate with colleagues from all around the world.

I am grateful to my second examiner, \Prof{} \Dr{} Pierre Gentine, for his
great advice and feedback on my work.

My sincere thanks go to all my co-authors, namely \Prof{} \Dr{} Gustau
Camps-Valls, \Prof{} \Dr{} Veronika Eyring, \Prof{} \Dr{} Pierre
Friedlingstein, \Prof{} \Dr{} Pierre Gentine, \Dr{} Axel Lauer, \Prof{} \Dr{}
Markus Reichstein, and \Prof{} \Dr{} Steven Sherwood, for sharing their
expertise, their advice, and helpful comments on my studies.

I would like to thank \Prof{} \Dr{} Gustau Camps-Valls and his Image and Signal
Processing (ISP) group for hosting me during my research stay at the University
of Valencia. I really enjoyed the time there, where I had the opportunity to
meet great people and expand my knowledge about \acl{ML}.

Many thanks to \Dr{} Axel Lauer for being an amazing second author and for the
endless patience he showed whenever I had questions for him. I am also very
grateful to \Dr{} Birgit Hassler for her advice in all circumstances and for
providing the urgently-needed chocolate and cookies during long hours in the
office. A warm thank you to all my colleagues at DLR-EVA and IUP for their
professional advice, helpful discussions, and simply the great time we spent
together inside and outside of the office.

A special thank you to the \ac{ESMValTool} core development team for providing
me useful insights into modern software development and for the great workshops
and beers we shared.

@@

A very special thanks to the (extended) Langer family for their endless support
and advice in all situations of life.
